Parameterized convection, stratiform clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-28 resolution.tex
edits

The subtropics ($\pm (10^{\circ}-30^{\circ})$ latitude) are uniquely less sensitive to subsiding motion. This is likely due to the the large, global maximum in surface latent heat fluxes in the subtropics, which increases dilute CAPE above the threshold for convection, but is restricted from growing too much larger due to substantial subsiding motion aloft. These opposing influences result in small values of dilute CAPE, and the ZM scheme acts more like a shallow convection scheme, producing copious amounts of light precipitation or drizzle, irrespective of resolution. AGCMs are known to suffer from an excess of drizzle relative to observations \citep{D2006JCLIM}. \cite{XETAL2019JAMES} recently proposed a new convective trigger for the ZM scheme that the authors suggest may alleviate the excess drizzle bias in CAM. As with the ZM scheme used in this study that dilute CAPE exceed a threshold fro convection to ccur, \cite{XETAL2019JAMES} also requires dCAPE to be positive. Based on the analysis in this study, and the strong connection between vertical velocities and dCAPE reported in \cite{SZ2018JCLIM}, it is reasonable to speculate that dCAPE is often negative in drizzling regions. The authors suggest that the \cite{XETAL2019JAMES} trigger be explored as a means to mitigate the drizzling bias in CAM.

>>>>

The subtropics ($\pm (10^{\circ}-30^{\circ})$ latitude) are uniquely less sensitive to subsiding motion. This is likely due to the the large, global maximum in surface latent heat fluxes in the subtropics, which increases dilute CAPE above the threshold for convection, but is restricted from growing too much larger due to substantial subsiding motion aloft. These opposing influences result in small values of dilute CAPE, and the ZM scheme acts more like a shallow convection scheme, producing copious amounts of light precipitation or drizzle, irrespective of resolution. AGCMs are known to suffer from an excess of drizzle relative to observations \citep{D2006JCLIM}. \cite{XETAL2019JAMES} recently proposed a new convective trigger for the ZM scheme that the authors suggest may alleviate the excess drizzle bias in CAM. As with the ZM scheme used in this study, dilute CAPE must exceed a threshold for convection to occur, but \cite{XETAL2019JAMES} also requires dCAPE to be positive. Based on the analysis in this study, and the strong connection between vertical velocities and dCAPE reported in \cite{SZ2018JCLIM}, it is reasonable to speculate that dCAPE is often negative in drizzling regions, which would prevent the ZM scheme from triggering. The authors suggest that the \cite{XETAL2019JAMES} trigger be explored as a means to mitigate the drizzling bias in CAM.

{\color{red}{What follows needs serious work}}
